Sorting by Reversals

### 2020-07-04 slides.tex
update slides

\begin{proof}
We consider each case $b(\pi) - b(\pi \circ \rho) \in [-2, 2]$ separately.\pause
\begin{enumerate}
    \item A $2$-reversal removes at least one alternating cycle from the maximum alternating cycle decomposition.
        \begin{tabularx}{\textwidth}{XcX}
            \begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
            	\begin{pgfonlayer}{nodelayer}
            		\node [style=node] (0) at (-1.25, 0) {i};
            		\node [style=node] (1) at (1.25, 0) {j'};
            		\node [style=node] (2) at (3, 0) {i'};
            		\node [style=node] (3) at (-3, 0) {j};
            		\node (4) at (0, 0) {$\dots$};
            	\end{pgfonlayer}
            	\begin{pgfonlayer}{edgelayer}
            		\draw [style=blue edge, bend right] (3) to (1);
            		\draw [style=blue edge, bend left] (0) to (2);
            		\draw [style=red edge] (3) to (0);
            		\draw [style=red edge] (1) to (2);
            	\end{pgfonlayer}
            \end{tikzpicture} & $\rightarrow$ &
            \begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
            	\begin{pgfonlayer}{nodelayer}
            		\node [style=node] (0) at (-1.25, 0) {j'};
            		\node [style=node] (1) at (1.25, 0) {i};
            		\node [style=node] (2) at (3, 0) {i'};
            		\node [style=node] (3) at (-3, 0) {j};
            		\node (4) at (0, 0) {$\dots$};
            	\end{pgfonlayer}
            \end{tikzpicture}
        \end{tabularx}\pause

@@

\begin{corollary}[\citeauthor*{Christie1998}]
The only alternating cycle decomposition of $G(id)$ is $C = \emptyset$. \par
$R(C)$ consists of $n+1$ isolated blue vertices.
\end{corollary}

@@

\begin{tabularx}{\textwidth}{X|R}
$G(\pi)$ and $R(C)$ & $G(\pi \circ \rho(u))$ and $R(C_u)$ \\ \hline
\spadding\begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=node] (0) at (-3, 0) {0};
		\node [style=node] (1) at (-1.5, 0) {1};
		\node [style=node] (2) at (0, 0) {3};
		\node [style=node] (3) at (1.5, 0) {4};
		\node [style=node] (4) at (3, 0) {2};
		\node [style=node] (5) at (4.5, 0) {5};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw [style=red edge] (1) to (2);
		\draw [style=red edge] (3) to (4);
		\draw [style=red edge] (4) to (5);
		\draw [style=blue edge, bend right] (1) to (4);
		\draw [style=blue edge, bend left] (2) to (4);
		\draw [style=blue edge, bend left] (3) to (5);
	\end{pgfonlayer}
\end{tikzpicture} &
\begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=node] (0) at (-3, 0) {0};
		\node [style=node] (1) at (-1.5, 0) {1};
		\node [style=node] (2) at (0, 0) {2};
		\node [style=node] (3) at (1.5, 0) {4};
		\node [style=node] (4) at (3, 0) {3};
		\node [style=node] (5) at (4.5, 0) {5};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw [style=red edge] (2) to (3);
		\draw [style=red edge] (4) to (5);
		\draw [style=blue edge, bend left] (2) to (4);
		\draw [style=blue edge, bend left] (3) to (5);
	\end{pgfonlayer}
\end{tikzpicture}\\
\spadding\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=red node] (0) at (0, 1) {$\{2,3\}$};
		\node [style=red node] (1) at (-2, 1) {$\{1,2\}$};
		\node [style=blue node] (2) at (-1, -1) {$\{4,5\}$};
		\node [style=blue node] (3) at (2, -1) {$\{3,4\}$};
		\node [style=blue node] (4) at (2, 1) {$\{0,1\}$};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw (0) to (2);
		\draw (1) to (2);
	\end{pgfonlayer}
\end{tikzpicture} &
\spadding\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=red node] (0) at (0, 1) {$\{2,3\}$};
		\node [style=blue node] (1) at (-2, 1) {$\{1,2\}$};
		\node [style=red node] (2) at (-1, -1) {$\{4,5\}$};
		\node [style=blue node] (3) at (2, -1) {$\{3,4\}$};
		\node [style=blue node] (4) at (2, 1) {$\{0,1\}$};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw (0) to (2);
	\end{pgfonlayer}
\end{tikzpicture}
\end{tabularx}
\end{exampleblock}

@@

@@

\begin{lemma}[\citeauthor*{Christie1998}]
$R(C)$ contains no isolated blue vertices arising from cycles in $C$.
\end{lemma}\pause

\begin{lemma}[\citeauthor*{Christie1998}]
\label{lem:7}
Vertices arising from an unoriented $2$-cycle of $C$ must be in a connected component of $R(C)$ with vertices arising from at least one more alternating cycle of $C$.
\end{lemma}\pause

>>>>

\begin{proof}
To show: $b(\pi) - b(\pi \circ \rho) + c(\pi \circ \rho) - c(\pi) \leq 1$. \par
We consider each case $b(\pi) - b(\pi \circ \rho) \in [-2, 2]$ separately.\pause
\begin{enumerate}
    \item A $2$-reversal removes at least one alternating cycle from the maximum alternating cycle decomposition.
        \begin{tabularx}{\textwidth}{XcX}
            \begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
            	\begin{pgfonlayer}{nodelayer}
            		\node [style=node] (0) at (-1.25, 0) {i};
            		\node [style=node] (1) at (1.25, 0) {j'};
            		\node [style=node] (2) at (3, 0) {i'};
            		\node [style=node] (3) at (-3, 0) {j};
            		\node (4) at (0, 0) {$\dots$};
            	\end{pgfonlayer}
            	\begin{pgfonlayer}{edgelayer}
            		\draw [style=blue edge, bend right] (3) to (1);
            		\draw [style=blue edge, bend left] (0) to (2);
            		\draw [style=red edge] (3) to (0);
            		\draw [style=red edge] (1) to (2);
            	\end{pgfonlayer}
            \end{tikzpicture} & $\rightarrow$ &
            \begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
            	\begin{pgfonlayer}{nodelayer}
            		\node [style=node] (0) at (-1.25, 0) {j'};
            		\node [style=node] (1) at (1.25, 0) {i};
            		\node [style=node] (2) at (3, 0) {i'};
            		\node [style=node] (3) at (-3, 0) {j};
            		\node (4) at (0, 0) {$\dots$};
            	\end{pgfonlayer}
            \end{tikzpicture}
        \end{tabularx}\pause

@@

Observation: The only alternating cycle decomposition of $G(id)$ is $C = \emptyset$.\pause

\begin{corollary}[\citeauthor*{Christie1998}]
$R(C)$ consists of $n+1$ isolated blue vertices.
\end{corollary}

@@

\begin{tabularx}{\textwidth}{X|R}
$G(\pi)$ and $R(C)$ & $G(\pi \circ \rho(u))$ and $R(C_u)$ \\ \hline
\spadding\begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=node] (0) at (-3, 0) {0};
		\node [style=node] (1) at (-1.5, 0) {1};
		\node [style=node] (2) at (0, 0) {3};
		\node [style=node] (3) at (1.5, 0) {4};
		\node [style=node] (4) at (3, 0) {2};
		\node [style=node] (5) at (4.5, 0) {5};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw [style=red edge] (1) to (2);
		\draw [style=red edge] (3) to (4);
		\draw [style=red edge] (4) to (5);
		\draw [style=blue edge, bend right] (1) to (4);
		\draw [style=blue edge, bend left] (2) to (4);
		\draw [style=blue edge, bend left] (3) to (5);
	\end{pgfonlayer}
\end{tikzpicture} &
\onslide<2->{\begin{tikzpicture}[scale=0.6, every node/.style={scale=0.6}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=node] (0) at (-3, 0) {0};
		\node [style=node] (1) at (-1.5, 0) {1};
		\node [style=node] (2) at (0, 0) {2};
		\node [style=node] (3) at (1.5, 0) {4};
		\node [style=node] (4) at (3, 0) {3};
		\node [style=node] (5) at (4.5, 0) {5};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw [style=red edge] (2) to (3);
		\draw [style=red edge] (4) to (5);
		\draw [style=blue edge, bend left] (2) to (4);
		\draw [style=blue edge, bend left] (3) to (5);
	\end{pgfonlayer}
\end{tikzpicture}}\\
\spadding\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=red node] (0) at (0, 1) {$\{2,3\}$};
		\node [style=red node] (1) at (-2, 1) {$\{1,2\}$};
		\node [style=blue node] (2) at (-1, -1) {$\{4,5\}$};
		\node [style=blue node] (3) at (2, -1) {$\{3,4\}$};
		\node [style=blue node] (4) at (2, 1) {$\{0,1\}$};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw (0) to (2);
		\draw (1) to (2);
	\end{pgfonlayer}
\end{tikzpicture} &
\onslide<3->{\spadding\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=red node] (0) at (0, 1) {$\{2,3\}$};
		\node [style=blue node] (1) at (-2, 1) {$\{1,2\}$};
		\node [style=red node] (2) at (-1, -1) {$\{4,5\}$};
		\node [style=blue node] (3) at (2, -1) {$\{3,4\}$};
		\node [style=blue node] (4) at (2, 1) {$\{0,1\}$};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw (0) to (2);
	\end{pgfonlayer}
\end{tikzpicture}}
\end{tabularx}
\end{exampleblock}

@@

\begin{corollary}[\citeauthor*{Christie1998}]
$R(C)$ contains no isolated blue vertices arising from cycles in $C$.
\end{corollary}\pause

@@

\begin{lemma}[\citeauthor*{Christie1998}]
\label{lem:7}
Vertices arising from an unoriented $2$-cycle of $C$ must be in a connected component of $R(C)$ with vertices arising from at least one more alternating cycle of $C$.
\end{lemma}

\begin{center}
\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
	\begin{pgfonlayer}{nodelayer}
		\node [style=node] (0) at (-3, 0) {};
		\node [style=node] (1) at (-1.25, 0) {};
		\node [style=node] (2) at (1.25, 0) {};
		\node [style=node] (3) at (3, 0) {};
		\node (4) at (0, 0) {$\dots$};
		\node (5) at (-4.25, 0) {$\dots$};
		\node (6) at (4.25, 0) {$\dots$};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw [style=blue edge, bend left] (0) to node[sloped,midway,above] {u} (3);
		\draw  [style=blue edge, bend right](1) to node[sloped,midway,below] {v} (2);
		\draw [style=red edge] (0) to (1);
		\draw [style=red edge] (2) to (3);
	\end{pgfonlayer}
\end{tikzpicture}
\end{center}\pause
